Boundary Labeling for annotated documents

### 2018-02-23 LaTeX/Paper.tex
Paper: Wrote computation time analysis for graph creation algorithm. Re-introduced and edited graph-creation pseudocode. Program: No changes.

\chapter{The Algorithm}
%1 Zeile Einleitung hier einfügen - zb: Kapitelübersicht
\section{Problem Specification}
We limited the leaders to use exclusively O- and P-Segments, and banned them from passing through words. We also place labels as far up as possible to maximize the space remaining for  remaining placements. Additionally, a leader isn't allowed to be any longer as is necessary to connect a given Site with its label's port.

@@

\begin{itemize}
 \item Computation time of graph-creation
 \item Computation time of the routing algorithm for single leaders
 \item Overall computation time of the routing algorithm
\end{itemize}
~\\
Furthermore, we will prove that:
\begin{itemize}
\item The algorithm always returns a shortest path
\item The algorithm generates only crossing-free routings
\item The algorithm places as many annotations as possible
\item The algorithm keeps the annnotations in reading order
\end{itemize}

%\begin{algorithm}%{r}{0.35\textwidth}
%\DontPrintSemicolon
%\SetKwData{Words}{words}
%\SetKwData{PrevW}{previousWord}
%\SetKwData{G}{Graph}
%\SetKwData{W}{w} \SetKwData{V}{v}\SetKwData{Va}{v1} \SetKwData{Vb}{v2} \SetKwData{Vc}{v3} \SetKwData{Vd}{v4}
%\SetKwData{Up}{UpperVerticesList}
%\SetKwData{Low}{LowerVerticesList}
%
%\SetKwFunction{setAnn}{setAnnotation}
%\SetKwFunction{NewVert}{new Vertex}
%\SetKwFunction{AddVert}{addVertex}
%\SetKwFunction{AddAll}{addAll}
%\SetKwFunction{CEdge}{createEdgeBetween}
%\SetKwFunction{PosConn}{connectBasedOnPosition}
%\SetKwFunction{ClrList}{emptyList}
%\SetKwFunction{getC}{getCenter}
%\SetKwFunction{tLeft}{getTopLeft}
%\SetKwFunction{tRight}{getTopRight}
%\SetKwFunction{bLeft}{getBottomLeft}
%\SetKwFunction{bRight}{getBottomRight}
%\SetKwFunction{Newline}{startNewLine}
%
%\KwData{A text with annotations,stored as a String-Array}
%\KwResult{A Graph (as described above)}
%
% initialization\;
% 
% \ForEach{\W in \Words}{
%  \eIf{\W is annotation}{
%   \V$\gets$\NewVert{\PrevW.\getC{}}\;
%   \V.\setAnn{\W}\;
%   \G.\AddVert{\V}\;
%   \Up.\AddVert{\V}\;
%  }{
%   \If{\W is too big for the line}{
%    \Newline{}\;
%    \PosConn{\Up}\;
%    \Up$\gets$\Low\;
%    \ClrList{\Low}\;
%   }
%   \Va $\gets$\NewVert{\W.\tLeft{}}\;
%   \Vb $\gets$\NewVert{\W.\tRight{}}\;
%   \Vc $\gets$\NewVert{\W.\bLeft{}}\;
%   \Vd $\gets$\NewVert{\W.\bRight{}}\;
%   \;
%   \G.\AddAll{\Va,\Vb,\Vc,\Vd}\;
%   \Up.\AddAll{\Va,\Vb}\;
%   \Low.\AddAll{\Vc,\Vd}\;
%   \G.\CEdge{\Va,\Vc}\;
%   \G.\CEdge{\Vb,\Vd}\;
%  }
% } 
%\caption{Representation of the Graph-creation algorithm in pseudocode}
%\label{alg:GraphCreation}
%\end{algorithm}

>>>>

\chapter{The Algorithm}
%1 Zeile Einleitung hier einfügen - zb: Kapitelübersicht
\section{Problem Specification}
\label{sec:ProbSpec}
We limited the leaders to use exclusively O- and P-Segments, and banned them from passing through words. We also place labels as far up as possible to maximize the space remaining for  remaining placements. Additionally, a leader isn't allowed to be any longer as is necessary to connect a given Site with its label's port.

@@

\begin{itemize}
 \item Computation time of graph-creation
 \item Computation time of the routing algorithm for single leaders
 \item Overall computation time of the routing algorithm
\end{itemize}
~\\
Furthermore, we will prove that:
\begin{itemize}
\item The algorithm generates only crossing-free routings
\item The algorithm always returns a highest (define!) legal path

NOTE: The algorithm keeps the annnotations in reading order
\end{itemize}

To determine the program's computation time, we will first take a look at the creation of the graph. As discussed in section~\ref{sec:ProbSpec}, we will be placing a pair of vertices per whitespace character, as well as one additional pair at both the start and end of each line, which amounts to $2\times|H|+4\times|L|$ vertices total. Together with the sites $I$, which are also represented as vertices, this results in the total number of vertices $|V|=|I|+2\times|H|+4\times|L|$. Additionally, each vertex in a pair is connected to its counterpart, which creates $(|V|-|I|)/2$ edges, representing all possible P-Segments. Finally, each edge placed in a space $s \in S$ above or below a line will be connected to each other, which is solved by connecting each vertex to the next unconnected vertex remaining in $s$. This leads to the creation of $|s|-1$ edges representing possible P-segments, which leads to a total of $|V|-|S|$ additional edges, making the total number of edges $|E|=(3\times|V|-2\times|S|-|I|)/2$.%Todo: look up fractions.
If we assume that the creation of edges and vertices both take a similar amount of time, we are looking at roughly $5/2 \times |V|$ operations, which means that the algorithm scales linearly with the amount of vertices placed, which in turn is directly proportional to the number of words $|W|$ in the text.
For a representation of the graph-generation algorithm in pseudocode, see Alg.~\ref{alg:GraphCreation}.

\begin{algorithm}
\DontPrintSemicolon
\SetKwData{Words}{words}
\SetKwData{PrevW}{previousWord}
\SetKwData{G}{Graph}
\SetKwData{W}{w} \SetKwData{V}{v}\SetKwData{Va}{v1} \SetKwData{Vb}{v2}
\SetKwData{Up}{UpperVerticesList}
\SetKwData{Low}{LowerVerticesList}

\SetKwFunction{setAnn}{setAnnotation}
\SetKwFunction{NewVert}{new Vertex}
\SetKwFunction{AddVert}{addVertex}
\SetKwFunction{AddAll}{addAll}
\SetKwFunction{CEdge}{createEdgeBetween}
\SetKwFunction{PosConn}{connectBasedOnPosition}
\SetKwFunction{ClrList}{emptyList}
\SetKwFunction{getC}{getCenter}
\SetKwFunction{tLeft}{getTopLeft}
\SetKwFunction{tRight}{getTopRight}
\SetKwFunction{bLeft}{getBottomLeft}
\SetKwFunction{bRight}{getBottomRight}
\SetKwFunction{Newline}{startNewLine}

\KwData{A text with annotations,stored as a String-Array}
\KwResult{A Graph (as described above)}

 initialization\;

 \ForEach{\W in \Words}{
  \eIf{\W is annotation}{
   \V$\gets$\NewVert{\PrevW.\getC{}}\;
   \V.\setAnn{\W}\;
   \G.\AddVert{\V}\;
   \Up.\AddVert{\V}\;
  }{
   \If{\W is too big for the line}{
    //Create last pair of vertices in current line\;
    \Va $\gets$\NewVert{\PrevW.\tRight{}}\;
    \Vb $\gets$\NewVert{\PrevW.\bRight{}}\;
    \G.\AddAll{\Va,\Vb}\;
    \Up.\AddVert{\Va}\;
    \Low.\AddVert{\Vb}\;
    \G.\CEdge{\Va,\Vb}\;
    \;
    //Start new line\;
    \Newline{}\;
    \PosConn{\Up}\;
    \Up$\gets$\Low\;
    \ClrList{\Low}\;
   }
   \Va $\gets$\NewVert{\W.\tLeft{}}\;
   \Vb $\gets$\NewVert{\W.\bLeft{}}\;
   \;
   \G.\AddAll{\Va,\Vb}\;
   \Up.\AddVert{\Va}\;
   \Low.\AddVert{\Vb}\;
   \G.\CEdge{\Va,\Vb}\;
  }
 } 
\caption{Representation of the Graph-creation algorithm in pseudocode}
\label{alg:GraphCreation}
\end{algorithm}
